\documentclass[12pt]{myucthesis}

%\nofiles
% The above command prevents latex from writing its auxiliary
% files. This is useful if you want to manually tweak them before you
% generate your final PDF.


% Page layout. The fancyhdr package may complain about the need for a
% larger headheight, depending on how long chapter titles are; if left
% unspecified in the geometry setup, it defaults to 12pt. The
% "showframe" option causes the geometry package (version >= 5.0) to
% show a frame around the margins on every page, which is great for
% checking that you don't overflow anywhere.

%\usepackage[letterpaper,includehead,margin=1in,headheight=15pt,showframe]{geometry}
\usepackage[letterpaper,includehead,margin=1in,headheight=15pt]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancyplain}
\lhead[\fancyplain{\thepage}{\thepage}]{\fancyplain{}{\scshape\rightmark}}
\rhead[\fancyplain{}{\scshape\leftmark}]{\fancyplain{\thepage}{\thepage}}
\chead{}
\cfoot{}
\lfoot{}
\rfoot{}


% Bibliography stuff:

\newcommand{\newblock}{\par} % need this for some natbib internal bug
\usepackage{natbib}
\citestyle{aa}
\bibliographystyle{yahapj}
\setlength{\bibsep}{0ex} % single-space entries
\def\bibpreamble{\addcontentsline{toc}{chapter}{Bibliography}} % get a good TOC entry


% Other setup:

\usepackage[T1]{fontenc} % see http://tinyurl.com/67zdxwf
\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue,pdfusetitle]{hyperref}
\usepackage{pdflscape} % allows landscape-oriented figures with PDF page rotation
\usepackage{aasmacros,amsmath,amssymb,graphicx}
\usepackage{mydeluxetable} % deluxetable customized to play well with ucthesis


\begin{document}
\ssp % single spacing
\hypersetup{pageanchor=false}
\include{setup}
\maketitle
\copyrightpage

\begin{abstract}
This thesis presents a systematic study of the relationships between
galaxy properties and their environments. Multi-wavelength
imaging and spectroscopic data are used to construct a large sample of
galaxy groups spanning nearly half the age of the Universe. Weak gravitational
lensing measurements enable a census of baryonic and dark matter in
these groups, and in particular, identification of halo centers. With
empirically determined centers of mass, trends in galaxy colors and
morphologies with groupcentric distance are studied to test models of
galaxy evolution.
\end{abstract}

\hypersetup{pageanchor=true}
\begin{frontmatter}

%\begin{dedication}
%\null\vfil
%{\large
%\begin{center}
%I dedicate this dissertation to graduate students everywhere.
%\end{center}}
%\null\vfil
%\end{dedication}

\tableofcontents
%\listoffigures % optional
%\listoftables % optional

% If using code.sty, can also add:
%% \listofcodes
%% \addcontentsline{toc}{chapter}{List of Code Examples}

\begin{acknowledgements}

Marc Davis once told me that \textit{``a thesis is not supposed to be your
best work; it's just practice.''} I hope he's right.

Still, I wish to thank a small portion of the many people who have
shaped my progress to this point. I am thankful to have had a
wonderful array of research collaborators. Alexie Leauthaud has been
an amazing mentor, guiding me through my early projects and sharing
her expertise. Kevin Bundy, Jeremy Tinker, and Alexis Finoguenov have
generously offered their hours and insights.

Thanks to my advisor, David Schlegel, for his guidance and enthusiasm,
for introducing me to endurance cycling, and for instilling an ethic
that it is better to ask forgiveness than permission. Thanks to Uros
Seljak for keeping me on my toes and exposing me to shellfish.  Thanks
to the other members of my committee, Chung-Pei Ma, Marc Davis,
and Saul Perlmutter for sharing their advice, experience, and tough
questions.

Thanks especially to Andrew Wetzel and Eric Huff for organizing a
cosmology discussion group and for many thoughtful conversations.
Thanks to the many other grad students and postdocs who have helped
with kicking around ideas, sharing their wisdom, and getting
outdoors, particularly Jessica Kirkpatrick, Jon Blazek, Nicholas
McConnell, Nic Ross, Beth Reid, and Ami Choi. Thanks to all the
denizens of Del Mar, and specifically Peter Williams for introducing me to
the house, to git, and to his
\href{https://github.com/pkgw/ucastrothesis}{\textsf{ucastrothesis}}
\LaTeX\ template. Thanks also to Katie Aspell for support and patience
while finishing up this year.

There are some other groups of people I would like to acknowledge that
played important roles in my time at Berkeley. First, the creators and
maintainers of the East Bay Regional Park District, where I have spent
many hours contemplating (and sometimes escaping) the contents of this
document.  Another large and largely unknown group to thank are the
developers of open source software tools used in my research. A third
important community to which I owe gratitude are the data collectors
and survey architects behind the COSMOS collaboration and the Sloan
Digital Sky Survey.

Finally, my deepest thanks to my family for all their support and
encouragement that helped me get here.

\end{acknowledgements}
\end{frontmatter}

\include{intro/intro}
\include{catalog/catalog}
\include{centering/centering}
\include{transformers/transformers}
%\include{flow/flow}
%\include{speclens/speclens}
%\include{outlook/outlook}
\bibliography{thesis}{}
\end{document}
